---
title: "BST 260 HW 0"
author: "Emily Thompson"
format: html
editor: visual
execute: 
    echo: false
---

## Exercises

(@) *Write a Quarto document that defines variables $a=1, b=3, c=2$
and print out the solutions to $f(x) = ax^2+bx+c=0$. Do not report complex solutions, only real numbers.* 

```{r}
a <- 1
b <- 3
c <- 2

#set solutions equal to NA if complex
x1 <- ifelse((b^2-4*a*c)<0, NA, (-b+sqrt(b^2-4*a*c))/2*a)
x2 <- ifelse((b^2-4*a*c)<0, NA, (-b-sqrt(b^2-4*a*c))/2*a)

print.solutions <- function(x1, x2){
  if (!is.na(x1) & !is.na(x2)){print(paste0("The solutions are " , x1 , " and " , x2, "."))} 
  else if (x1==x2){print(paste0("The solution is ", x1, "."))}
  else{print("There are no real solutions.")}
}

print.solutions(x1, x2)

```
These solutions to $f(x) = ax^2+bx+c=0$ are based on input values of $a=`r a`, b=`r b`$, and $c=`r c`$.

(@) *Include a graph of $f(x)$ versus $x$ for $x \in (-5,5)$.*
```{r}
x<- seq(-5, 5, length=300)
plot(x, a*x^2 + b*x+c, type="l")
abline(h=0, lty=2)
```
The graph displays the solution(s) to the equation (if any) as the point(s) where the curve crosses the line at $y=0$.



